### 2012-04-06 doc/theses/mikula/conclusion.tex
Master thesis: In progress.
Master thesis: Corrections.

\chapter{Conclusion}
The aim of this thesis was to employ XML operations in the XML schema inference. We analyzed several existing methods of the XML schema inference and we searched for methods that utilize some XML operations. We found only one method, inferring keys from XQuery queries.

@@

Before a creation of the algorithm itself, we had to take several decisions in questions that emerged. Since there is a lack of the methods dealing with the utilisation of XML operation, there is also a lack of practically proven solutions that can help in such decision making.

@@

We also implemented several ideas from the overview to infer XSD built-in types of elements and attributes. And we extended the one existing method dealing with the inference of keys. We experimentally demonstrated that on some input files, results of the extended method are better than results of the original method. However, we did not succeed in a search of an ideal, large enough set of test data. The testing was performed on a small set of input queries and further testing and algorithm tuning is required.

@@

\todo[inline]{Nejake prehladne zhrnutie plusov a minusov?}
\todo[inline]{testy}

\section{Future Work}
This work implements only some ideas discussed in the overview in Chapter \ref{CHAPTER_analysis_of_xquery}, leaving most of them for a future work. Also, the implemented algorithms can be further refined as was already mentioned in Chapter \ref{CHAPTER_proposed_algorithm} with the presentation of the algorithms. For example thorough processing of user-defined function calls.

@@

The utilization of XQuery queries certainly provides a space for incorporating an interaction with user. For example, a user may influence the scoring of inferred keys to get more precise results.

>>>>

\chapter{Conclusion}
The aim of this thesis was to employ XML operations in the XML schema inference process. We analyzed several existing methods of the XML schema inference and we searched for methods that utilize selected XML operations. We found only one method, inferring keys from XQuery queries.

@@

Before creation of the algorithm itself, we had to take several decisions in questions that emerged. Since there is a lack of the methods dealing with the utilisation of XML operation, there is also a lack of practically proven solutions that can help in such decision making.

@@

We also implemented several ideas from the overview to infer XSD built-in types of elements and attributes. And we extended and implemented the one existing method dealing with the inference of keys. We experimentally demonstrated that on some input files, results of the extended method are better than results of the original method. However, we did not succeed in the search of an ideal, large enough set of test data. The testing was performed on a small set of input queries and further testing and algorithm tuning is required.

@@

\todo[inline]{Nejake prehladne zhrnutie plusov a minusov? ANO}

\section{Future Work}
This work implements only some ideas discussed in the overview in Chapter \ref{CHAPTER_analysis_of_xquery}, leaving most of them for future work. Also, the implemented algorithms can be further refined as was already mentioned in Chapter \ref{CHAPTER_proposed_algorithm} with the presentation of the algorithms. For example thorough processing of user-defined function calls.

@@

The utilization of XQuery queries certainly provides a space for incorporating interaction with user. For example, a user may influence the scoring of inferred keys to get more precise results.

### 2012-04-06 doc/theses/mikula/diplomka.tex
Master thesis: Corrections.

Abstrakt: \todo[inline]{TODO cca 10-15 riadkov}
% abstrakt v rozsahu 80-200 slov; nejedná se vąak o opis zadání diplomové práce

Klíčová slova: \todo[inline]{TODO 5-8 slov}
% 3 aľ 5 klíčových slov

@@

Abstract: \todo[inline]{TODO}
% abstrakt v rozsahu 80-200 slov v angličtině; nejedná se vąak o překlad
% zadání diplomové práce

Keywords: \todo[inline]{TODO}
% 3 aľ 5 klíčových slov v angličtině

>>>>

Abstrakt: V poslednej dobe bolo vyvinutých množstvo metód zaoberajúcich sa automatickým odvodzovaním XML schémy. Väčšina z nich ale používa XML dokumenty ako jediný vstup. My sa v tejto práci zameriavame na rozšírenie odvo\-dzo\-vania zahrnutím XML operácií, konkrétne XQuery dotazov. Diskutujeme ako je možné využiť XQuery dotazy na vylepšenie procesu odvodzovania a navrhujeme algoritmus založený na vybraných vylepšeniach, ktorý rozširuje existujúcu metódu hľadania kľúčov a ktorý môže byť začlenený do tzv. \emph{metód odvodzujúcich gramatiku}. Implementovaním algoritmu sme vytvorili prvé kompletné riešenie odvodzovania XML schémy, ktoré využíva XML dokumenty spolu s XML operáciami.
% abstrakt v rozsahu 80-200 slov; nejedná se vąak o opis zadání diplomové práce

Klíčová slova: XML, XML schéma, odvozování, XQuery, dotazy, XML operace
% 3 aľ 5 klíčových slov

@@

Abstract: Recently, plenty of methods dealing with automatic inference of XML schema have been developed, however, most of them utilize XML documents as their only input. In this thesis we focus on extending inference by incorporating XML operations, in particular XQuery queries. We discuss how can XQuery queries help in improving the inference process and we propose an algorithm based on chosen improvements, extending an existing method of a key discovery, that can be integrated to so-called \emph{grammar-inferring} methods. By implementing it, we created the first solution of XML schema inference using XML documents along with XML operations.
% abstrakt v rozsahu 80-200 slov v angličtině; nejedná se vąak o překlad
% zadání diplomové práce

Keywords: XML, XML schema, inference, XQuery, queries, XML operations
% 3 aľ 5 klíčových slov v angličtině

### 2012-04-06 doc/theses/mikula/experiments.tex
Master thesis: Corrections.

\todo[inline]{Mozno popisat aj vyznam tychto dotazov?}

@@

Results of this test scenario are shown in Tables \ref{TAB_inferred_types_b}, \ref{TAB_inferred_keys_b}, and \ref{TAB_inferred_negative_uniqueness_statements_b}. All seams to be as we expected.

@@

We demonstrated that also the original method works and we can get better results with little larger input dataset. Though, this set is still very small and we do not show how the methods works with large real-world data, possibly containing FLWOR constructs not satisfying our assumption that each join is done by a key/foreign key pair.

We attach the resulting XML Schema in Appendix \ref{listing_xsd}. It was made using threshold 0.3. It means that all key statements with normalized weight equal or higher than 0.3 are considered correct and are included in the schema.

>>>>

@@

Results of this test scenario are shown in Tables \ref{TAB_inferred_types_b}, \ref{TAB_inferred_keys_b}, and \ref{TAB_inferred_negative_uniqueness_statements_b}. All seem to be as we expected.

@@

We demonstrated that also the original method works and we can get better results with little larger input dataset. Though, this set is still very small and we do not show how the methods work with large real-world data, possibly containing FLWOR constructs not satisfying our assumption that each join is done by a key/foreign key pair.

We attach the resulting XSD in Appendix \ref{listing_xsd}. It was made using threshold 0.3. It means that all key statements with normalized weight equal or higher than 0.3 are considered correct and are included in the schema.

### 2012-04-06 doc/theses/mikula/introduction.tex
Master thesis: Corrections.

In Chapter 5, we discusses some essential questions that we needed to decide before a development of an algorithm.

@@

An implementation of the proposed algorithm using a jInfer framework is described in Chapter 8. Chapter 9 then discusses performed experiments and their outcomes.

>>>>

In Chapter 5, we discuss some essential questions that we needed to decide before a development of an algorithm.

@@

An implementation of the proposed algorithm using the jInfer framework is described in Chapter 8. Chapter 9 then discusses performed experiments and their outcomes. And, finally, Chapter 10 concludes.

### 2012-04-06 doc/theses/mikula/proposed_algorithm.tex
Master thesis: Corrections.

\STATE $type :=$ UnknownType
\IF{$is(exprNode,$ LiteralNode$)$}
     \STATE $type :=$ XSD atomic type $exprNode.type$, exactly-once cardinality
\ELSIF{$is(exprNode,$ FunctionCallNode$)$}
     \STATE $type := getFunctionReturnType(exprNode.fncName)$
\ELSIF{$is(exprNode,$ VarRefNode$)$}
     \STATE $type := getVariableType(contextVarTypes, exprNode.varName)$
     \IF{$type$ is PathType}
         \STATE $step :=$ a path step (new instance of StepExprNode) representing the variable reference
		 \STATE $substeps :=$ an empty associative array         
         \STATE $substeps[step] := type$
         \STATE $pathExprNode :=$ new instance of PathExprNode containing one step step
         \STATE $type :=$ PathType containing $pathExprNode$ and $substeps$
     \ENDIF
\ELSIF{$is(exprNode,$ PathExprNode$)$}
     \STATE $type := createPathType(exprNode)$
\ELSIF{$is(exprNode,$ OperatorNode$)$}
     \STATE $type := determineOperatorType(exprNode, contextVarTypes)$
\ELSIF{$is(exprNode,$ FLWORExprNode$)$}
     \STATE $returnClauseNode := exprNode.getChild(ReturnClauseNode)$
     \STATE $type := createForUnboundType(getType(returnClauseNode))$
\ENDIF

@@

\section{Step 4: Key Discovery}
\todo[inline]{Tu by neskodilo napisat, ze sice preberame alg, ale ho aj implementujeme a overime, co v povodnom clanku nebolo.}
In this step, the algorithm discovers keys of elements, incorporating the approach from paper \cite{Necasky:2009:DXK:1529282.1529414}, described in Chapter \ref{Keys}, and extending it. Despite the approach was proposed, it has not been implemented yet. Therefore we will be the first to implement it and perform consecutive testing.

@@

Note that the restrictions placed on the paths $C$ and $P$ are less restrictive as in the case of keys. If we found a negative uniqueness statement ($C$, $P$), where $P$ or $C$ contains predicates, then it implies that also $(C', P')$ is a negative uniqueness statement, where $C'$ and $P'$ are $C$ and $P$ stripped of predicates. In the case of special function calls, the explanation is the same.

@@

\subsection{Normalization of Key Statements}
The original approach \cite{Necasky:2009:DXK:1529282.1529414} employs the following normalization which we adopt. Is also incorporates a heuristic for precision enhancement. For details, we refer to it.

>>>>

\STATE $type :=$ UnknownType
\IF{$is(exprNode,$ LiteralNode$)$}
     \STATE $type :=$ XSD atomic type $exprNode.type$, exactly-once cardinality
\ELSIF{$is(exprNode,$ FunctionCallNode$)$}
     \STATE $type := getFunctionReturnType(exprNode.fncName)$
\ELSIF{$is(exprNode,$ VarRefNode$)$}
     \STATE $type := getVariableType(contextVarTypes, exprNode.varName)$
     \IF{$type$ is PathType}
         \STATE $step :=$ a path step (new instance of StepExprNode) representing the variable reference
		 \STATE $substeps :=$ an empty associative array         
         \STATE $substeps[step] := type$
         \STATE $pathExprNode :=$ new instance of PathExprNode containing one step
         \STATE $type :=$ PathType containing $pathExprNode$ and $substeps$
     \ENDIF
\ELSIF{$is(exprNode,$ PathExprNode$)$}
     \STATE $type := createPathType(exprNode)$
\ELSIF{$is(exprNode,$ OperatorNode$)$}
     \STATE $type := determineOperatorType(exprNode, contextVarTypes)$
\ELSIF{$is(exprNode,$ FLWORExprNode$)$}
     \STATE $returnClauseNode := exprNode.getChild(ReturnClauseNode)$
     \STATE $type := createForUnboundType(getType(returnClauseNode))$
\ENDIF

@@

\section{Step 4: Key Discovery}
In this step, the algorithm discovers keys of elements, incorporating the approach from paper \cite{Necasky:2009:DXK:1529282.1529414}, described in Chapter \ref{Keys}, and extending it. Despite the approach was proposed, it has not been implemented yet. Therefore we will be the first to implement it and perform consecutive testing.

@@

Note that the restrictions placed on the paths $C$ and $P$ are less restrictive than in the case of keys. If we find a negative uniqueness statement ($C$, $P$), where $P$ or $C$ contains predicates, then it implies that also $(C', P')$ is a negative uniqueness statement, where $C'$ and $P'$ are $C$ and $P$ stripped of predicates. In the case of special function calls, the explanation is the same.

@@

\subsection{Normalization of Key Statements}
The original approach \cite{Necasky:2009:DXK:1529282.1529414} employs the following normalization which we adopt. It also incorporates a heuristic for precision enhancement. For details, we refer to it.
